### 2024-08-01 paper/supplementary.tex
final cleanup

\noindent\boldblue{\large{Supplementary A: High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel.png}
    \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.66,31.47], p = 0.565) \boldblue{B)} Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see Supplementary Figure 6). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig. 2}). \boldblue{C)} Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) \boldblue{D)} Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open gray circles and connecting lines represent individual data.}
\end{figure}

@@

\noindent Here we define the parameters used for the three models. Note that not all the parameters are used in each model, which we specify further below and in \boldblue{Fig. 2}. The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement. Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset. Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target. Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{A}$) of the stimulus’s movement onset distribution. Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended transition time, $\tau$. Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing. All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.  Each of our three models has a different set of known and unknown parameters. A model decision policy has full knowledge of known parameters when determining the optimal decision time. A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.

@@

\noindent The Partial Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, and stimulus movement onset. This model had the following unknown parameters: switch time mean and uncertainty, and timing uncertainty. The Partial Switch Time Model reflects our hypothesis that participants do not account for the delay and uncertainties associated with guessing.

@@

\noindent We begin by defining the general normal probability density function and cumulative density function:
\setlength{\belowdisplayskip}{4pt} \setlength{\belowdisplayshortskip}{4pt} % THIS MUST BE HERE FOR EQUATIONS SPACING
\setlength{\abovedisplayskip}{4pt} \setlength{\abovedisplayshortskip}{4pt}
% Define pdf and cdf
\begin{equation}
    X\sim\mathcal{N}(\mu,\sigma)
\end{equation}
\begin{equation}
    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
\end{equation}

@@

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq. 5}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq. 6}).
% Define random variables S and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

Consider $s$ and $t$ as the realizations of random variables $S$ and $T$ for a single trial. On any specific trial, a decision-maker will react if the stimulus movement onset is before the transition time (i.e., $s<t$). Conversely, the decision-maker will guess at the transition time if the stimulus has not moved by the transition time (i.e., $s>t$). Thus, the probability that a participant will react or guess depends on the participants choice of a transition time $\tau$. Specifically, the probability that the participant will react is the probability that the random variable A is less than T.
% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(T>S)
\end{equation}

Since the participants can only react or guess, the probability of guessing is simply one minus the probability of reacting.
\begin{equation}
    P(Guess|\tau) = P(T<S)
\end{equation}

@@

The mean of the truncated stimulus movement onset distribution ($\mu_{S_{react}}$) can be calculated by combining the indicator function and the method of moments. We start by calculating the expected value of the random variable $S$, which is the integral from $-\infty$ to $\infty$ of the value $s$ multiplied by the probability density function $f_{S}(s)$.
% Define expected value
\begin{equation}
    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s)ds
\end{equation}

Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution. For the truncated stimulus movement onset distribution, we only take values $s$ if they are less than $t$. Since the inclusion of $s$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $s$ and $t$. Inside the double integral, we multiply the realized value $s$ by its probability density function (i.e., $f_{S}(s)$). We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{s<t}$). Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that A is less than T. The mean (first moment) of the truncated stimulus movement onset distribution is
% Define Cutoff react mean 
\begin{equation}
    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}
\end{equation}

Similarly, we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
%
\begin{equation}
    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}
\end{equation}

The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing. Importantly, reacting and guessing have unique delays and uncertainties. Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
The participant mean reaction movement onset ($\mu_{mo_{react}}$, \boldblue{Eq. 14}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$). Likewise, the standard deviation of participant reaction movement onset ($\sigma_{mo_{react}}$, \boldblue{Eq. 15}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{A_{react}}$) plus the participant response time variance ($\sigma_{rt}^2$).
% Movement Onset times
\begin{equation}
    \mu_{mot_{react}} = \mu_{S_{react}} + \mu_{rt}
\end{equation}
\begin{equation}
    \sigma_{mot_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
\end{equation}

Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mot_{guess}}$, \boldblue{Eq. 16}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$. The participant standard deviation guess movement onset ($\sigma_{mot_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\boldblue{Eq. 17}).
%
\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
\end{equation}

Crucially, for the Known Switch Time Model and Unknown Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
% Switch time included in movement onset times
\begin{equation}
    \mu_{mot_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{mot_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
\end{equation}

For both the known switch time model and unknown switch time models, the switch time mean and uncertainty influence the model outputs. However, the decision policy of the Full Switch Time Model has perfect knowledge of the switch time, while the decision policy of the Partial Switch Time Model has imperfect knowledge of the switch time. Further below (see Model Fitting), we address how we estimate the amount of imperfect knowledge for the Partial Switch Time Model.

We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach}{guess}$) and standard deviation ($\sigma_{reach_{guess}}$) as
% Target Reach Time 
\begin{align}
    \mu_{reach_{react}} =\mu_{mot_{react}} + \mu_{mt}                      \\
    \sigma_{reach_{react}} = \sqrt{\sigma_{mot_{react}}^2 + \sigma_{mt}^2} \\
    \mu_{reach_{guess}} =\mu_{mot_{guess}} + \mu_{mt}                      \\
    \sigma_{reach_{guess}} = \sqrt{\sigma_{mot_{guess}}^2 + \sigma_{mt}^2}.
\end{align}

To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to
% Reach random variables
\begin{align}
    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \\
    \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
\end{align}

@@

We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect. The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from Eqs. 20-21. An indecision is simply the probability that the participant reaches the target after the time constraint:
% Probability of indecision sequence 
\begin{equation}
    P(Indecision|React) = 1 - P(Reach|React)
\end{equation}
\begin{equation}
    P(Indecision|Guess) = 1 - P(Reach|Guess)
\end{equation}

To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$). The probability of selecting the correct target when the participant reacts is 100\% (\boldblue{Eq. 24}). The probability of selecting the correct target when the participant guesses is 50\% (\boldblue{Eq. 25}).
% Probability of being correct
\begin{equation}
    P(Correct|React) = 1.0
\end{equation}
\begin{equation}
    P(Correct|Guess) = 0.5
\end{equation}

@@

Finally, we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\boldblue{Eq. 27-34}) and the probability of reaching and guessing given a transition time ($\tau$), as
\begin{align}
    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess).
\end{align}

@@

\noindent For each model, the goal of the decision policy is to find the optimal transition time that maximizes expected reward. The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
% Expected Reward
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is
%
\begin{align}
    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}
\end{align}

The decision policy uses known parameters to select an optimal transition time $\tau^*$ that maximizes expected reward:
% Maximize expected reward with tau
\begin{equation}
    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)]
\end{equation}

@@

We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$, switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).

@@

\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ (\autocite*{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.  Here the remaining parameters estimated from experimental data were set as the group level means. We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means ($Data_{i,j}$) according to
% Loss Equation 
\begin{equation}
    \mathcal{L} = \sum_{i = 1}^{6} \sum_{j = 1}^{5} \frac{|Data_{i,j} - Model_{i,j}|}{Data_{i,j}},
\end{equation}
where $i$ corresponds to experimental condition and $j$ corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects) over the target metrics. This fitting procedure was repeated 1,000 times to avoid local minimums. From these 1,000 optimizations, we used the set of parameters that resulted in the lowest loss as the initial guess for our bootstrap procedure. Model fitting was performed using the Powell algorithm in the Minimize function from the Scipy Python library. The parameter set with the lowest loss was used as the initial guess for the bootstrap procedure.

@@

The Partial Switch Time Model fit the timing uncertainty, switch time mean, switch time uncertainty. Critically, this model did not have full knowledge of these parameters, so the value that the decision policy used to select the optimal time was fit separately from the value that was used to determine the model outputs. Note that the timing uncertainty value used for model outputs is from experimental data, but this model allowed the knowledge of the timing uncertainty to be a fit parameter. The values that were used for model outputs were: timing uncertainty (77.83 ms; [69.4, 86.8]), switch time mean (21.10 ms; [1.46, 63.71]), switch time uncertainty (134.73 ms; [111.22, 155.06]. The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]). Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and transition time certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.

>>>>

\noindent\boldblue{\large{Supplementary A: High Variance Results}}
\begin{figure}[H]
    \centering
    \includegraphics[scale =1]{figures/exp1_movement_onset_panel_all_conditions.png}
    \caption*{\boldblue{Supplementary Figure 1: Timing Behaviour.} \boldblue{A)} Average participant movement onset (y-axis) for each experimental condition (x-axis). We found a significant main effect of stimulus movement onset mean (F[1.55,29.48] = 4.36, p = 0.030) and variance (F[1.00,19.00], p = 0.017)) on participant movement onset. There was no significant interaction (F[1.66,31.47], p = 0.565) \boldblue{B)} Corresponding participant movement onset (y-axis) for the three different mean stimulus onsets (x-axis) when collapsed across variance. During the early mean conditions, participants had a high probability of reacting to the stimulus and reaching a target within the time constraint. For the middle mean conditions, participants often waited longer to react and had a later guess than the early mean conditions. Waiting longer to react and/or late guessing led to later movement onset. In the late mean condition, participants waited to react to the stimulus, but ended up guessing a majority of the time (see \boldblue{Supplementary Figure 6}). The combination of waiting for the stimulus and eventually guessing, led to an earlier movement onset compared to the middle mean condition. For both the middle mean and late mean conditions, late guessing often led to indecisions (see \boldblue{Fig. 2}). \boldblue{C)} Participant movement onset standard deviation (y-axis) for each experimental condition (x-axis). We found a significant main effect of mean (F[1.38, 26.28], p = 0.018) and variance (F[1.00,19.00], p < 0.001) on participant movement onset standard deviation There was no significant interaction between stimulus movement onset mean and variance (F[1.98, 37.58], p = 0.097) \boldblue{D)} Corresponding participant movement onset standard deviation (y-axis) for the three different mean onsets (x-axis), when collapsed across variance. In the late mean conditions, waiting to react and then guessing led to a larger movement onset standard deviation compared to the early mean and middle mean conditions. Box and whisker plots display the 25th, 50th, and 75th percentiles. Open circles and connecting lines represent individual data.}
\end{figure}

@@

\noindent Here we define the parameters used for the three models. Note that not all the parameters are used in each model, which we specify further below and in \boldblue{Fig. 2}. The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement. Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset. Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target. Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{S}$) of the stimulus’s movement onset distribution. Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended transition time, $\tau$. Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing. All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.  Each of our three models has a different set of known and unknown parameters. A model decision policy has full knowledge of known parameters when determining the optimal decision time. A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.

@@

\noindent The Partial Switch Time Model had the following known parameters: response time mean and uncertainty, neuromechanical delay mean and uncertainty, movement time mean and uncertainty, and stimulus movement onset. This model had the following unknown parameters: switch time mean and uncertainty, and timing uncertainty. The Partial Switch Time Model reflects our hypothesis that participants can only partially account for the delay and uncertainties associated with guessing.

@@

\noindent We begin by defining the general normal probability density function and cumulative density function:
\setlength{\belowdisplayskip}{4pt} \setlength{\belowdisplayshortskip}{4pt} % THIS MUST BE HERE FOR EQUATIONS SPACING
\setlength{\abovedisplayskip}{4pt} \setlength{\abovedisplayshortskip}{4pt}

\setcounter{equation}{0}

% Define pdf and cdf
\begin{equation}
    X\sim\mathcal{N}(\mu,\sigma)
\end{equation}
\begin{equation}
    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F_{X}(b) = P(X \leq b) = \int_{-\infty}^{b} f_{X}(x; \mu, \sigma)dx
\end{equation}

@@

Next we define the mean and standard deviation of the participant movement onset separately for reaction decisions and guess decisions. We begin by defining $S$ as the random variable drawn from the stimulus’s movement onset distribution (\boldblue{Eq. 4}) and $T$ as the random variable drawn from the transition time distribution (\boldblue{Eq. 5}).
% Define random variables S and T
\begin{align}
    S & \sim\mathcal{N}(\mu_{S},\sigma_{S}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

Consider $s$ and $t$ as the realizations of random variables $S$ and $T$ for a single trial. On any specific trial, a decision-maker will react if the stimulus movement onset is before the transition time (i.e., $s<t$). Conversely, the decision-maker will guess at the transition time if the stimulus has not moved by the transition time (i.e., $s>t$). Thus, the probability that a participant will react or guess depends on the participants choice of a transition time mean ($\tau$). Specifically, the probability that the participant will react is the probability that the random variable T is greater than S.
% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(T>S).
\end{equation}

The probability that the participant will guess is the probability that the random variable T is less than S.
\begin{equation}
    P(Guess|\tau) = P(T<S).
\end{equation}

@@

The mean of the truncated stimulus movement onset distribution ($\mu_{S_{react}}$) can be calculated by combining the indicator function and the method of moments. We start by calculating the expected value of the random variable $S$, which is the integral from $-\infty$ to $\infty$ of the value $s$ multiplied by the probability density function $f_{S}(s)$.
% Define expected value
\begin{equation}
    \mu_{S} = \mathbb{E}[S] = \int_{-\infty}^{\infty}s \cdot f_{S}(s).ds
\end{equation}

Note that the expected value of the full stimulus movement onset distribution defined here is equivalent to the mean of the distribution. For the truncated stimulus movement onset distribution, we only take values $s$ if they are less than $t$. Since the inclusion of $s$ depends on $t$, we calculate the mean of the truncated stimulus movement onset distribution by integrating over every possible combination of $s$ and $t$. Inside the double integral, we multiply the realized value $s$ by its probability density function (i.e., $f_{S}(s)$). We also multiply the probability density function for $t$ (i.e., $f_{T}(t)$) and the indicator function ($\mathbbm{1}_{s<t}$). Since this double integral multiplies two gaussian probability density functions and only sums values if $s$ is less than $t$, we must normalize by dividing by the probability that S is less than T. The mean (first moment) of the truncated stimulus movement onset distribution is
% Define Cutoff react mean 
\begin{equation}
    \mu_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} s \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s \in S} \ dadt} {P(S<T)}.
\end{equation}

Similarly, we can find the standard deviation of the truncated stimulus movement onset distribution, where variance is the second moment, by:
%
\begin{equation}
    \sigma^2_{S_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (s - \mu_{S_{react}})^2 \cdot f_{S}(s) \cdot f_{T}(t) \cdot \mathbbm{1}_{s<t} \ ds \ dt}{P(S<T)}.
\end{equation}

The player’s movement onset distribution consists of a mix between reacting to the truncated stimulus movement onset and guessing. Importantly, reacting and guessing have unique delays and uncertainties. Thus, reaction decisions and guess decisions will lead to unique means and uncertainties of the participant movement onset distribution.
The participant mean reaction movement onset ($\mu_{mo_{react}}$, \boldblue{Eq. 12}) is the truncated stimulus movement onset mean ($\mu_{S_{react}}$) plus the participant mean response time ($\mu_{rt}$). Likewise, the standard deviation of participant reaction movement onset ($\sigma_{mo_{react}}$, \boldblue{Eq. 13}) is the square root of the variance of the truncated stimulus movement onset distribution ($\sigma_{S_{react}}^2$) plus the participant response time variance ($\sigma_{rt}^2$).
% Movement Onset times
\begin{equation}
    \mu_{mo_{react}} = \mu_{S_{react}} + \mu_{rt}
\end{equation}
\begin{equation}
    \sigma_{mo_{react}} = \sqrt{\sigma_{S_{react}}^2 + \sigma_{rt}^2}
\end{equation}

Here, $\mu_{rt}$ represents the time to process the stimulus movement plus the neuromechanical delay ($\mu_{nmd}$).
For the No Switch Time Model, the participant mean guess movement onset ($\mu_{mo_{guess}}$, \boldblue{Eq. 14}) is the sum of the participant transition time $\tau$ and the mean neuromechanical delay $\mu_{nmd}$. The participant standard deviation guess movement onset ($\sigma_{mo_{guess}}$) is the square root of the sum of the timing variance $\sigma_{\tau}^2$ and neuromechanical delay variance $\sigma_{nmd}^2$ (\boldblue{Eq. 15}).
%
\begin{equation}
    \mu_{mo_{guess}} = \tau +  \mu_{nmd}
\end{equation}
\begin{equation}
    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2}
\end{equation}

Crucially, for the Full Switch Time Model and Partial Switch Time Model, the mean and standard deviation of the guess movement onset includes the switch time mean and uncertainty,
% Switch time included in movement onset times
\begin{equation}
    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
\end{equation}

For both the Full Switch Time Model and Partial Switch Time Model, the switch time mean and uncertainty influence the model outputs. However, the decision policy of the Full Switch Time Model has perfect knowledge of the switch time, while the decision policy of the Partial Switch Time Model has imperfect knowledge of the switch time. Further below (see Model Fitting), we address how we estimate the amount of imperfect knowledge for the Partial Switch Time Model.

We define the react target reach time mean ($\mu_{reach_{react}}$) and standard deviation ($\sigma_{reach_{react}}$), and the  guess target reach time mean ($\mu_{reach_{guess}}$) and standard deviation ($\sigma_{reach_{guess}}$) as
% Target Reach Time 
\begin{align}
    \mu_{reach_{react}} =\mu_{mo_{react}} + \mu_{mt}                      \\
    \sigma_{reach_{react}} = \sqrt{\sigma_{mo_{react}}^2 + \sigma_{mt}^2} \\
    \mu_{reach_{guess}} =\mu_{mo_{guess}} + \mu_{mt}                      \\
    \sigma_{reach_{guess}} = \sqrt{\sigma_{mo_{guess}}^2 + \sigma_{mt}^2}.
\end{align}

To obtain the probability of reaching the target given the participant has either reacted ($X_{reach_{react}}$) or guessed ($X_{reach_{guess}}$), we need to define a random variable for the distribution of target reach times according to
% Reach random variables
\begin{align}
    X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \\
    X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}})
    % \hat{X}_{reach_{guess}} \sim \mathcal{N}(\hat{\mu}_{reach_{guess}}, \hat{\sigma}_{reach_{guess}}).
\end{align}

@@

We can now define the conditional probabilities for three outcome metrics: indecision, win, and incorrect. The conditional probability of an indecision given the participant has reacted ($P(Indecision|React)$) or guessed ($P(Indecision|Guess)$) follows immediately from \boldblue{Eqs. 24-25}. An indecision is simply the probability that the participant does not reach the target within the time constraint:
% Probability of indecision sequence 
\begin{equation}
    P(Indecision|React) = 1 - P(Reach|React)
\end{equation}
\begin{equation}
    P(Indecision|Guess) = 1 - P(Reach|Guess)
\end{equation}

To define a win or incorrect trial, we need the conditional probability of selecting the correct target given the participant has either reacted ($P(Correct|React)$) or guessed ($P(Correct|Guess)$). The probability of selecting the correct target when the participant reacts is 100\% (\boldblue{Eq. 28}). The probability of selecting the correct target when the participant guesses is 50\% (\boldblue{Eq. 29}).
% Probability of being correct
\begin{equation}
    P(Correct|React) = 1.0
\end{equation}
\begin{equation}
    P(Correct|Guess) = 0.5
\end{equation}

@@

Finally, we define the final probability of wins ($P(Win|\tau)$), indecisions ($P(Indecision|\tau)$), and incorrects ($P(Incorrect|\tau)$), by considering their and their associated conditional probabilities (\boldblue{Eq. 26-33}) and the probability of reaching and guessing given a transition time ($\tau$), as
\begin{align}
    P(Win|\tau)        = & P(React|\tau) \cdot P(Win|React) \nonumber        \\ &+  P(Guess|\tau) \cdot P(Win|Guess)\\
    P(Indecision|\tau) = & P(React|\tau) \cdot P(Indecision|React) \nonumber \\ &+ P(Guess|\tau) \cdot P(Indecision|Guess) \\
    P(Incorrect|\tau)  = & P(React|\tau) \cdot P(Incorrect|React) \nonumber  \\ &+ P(Guess|\tau) \cdot P(Incorrect|Guess).
\end{align}

@@

\noindent For each model, the goal of the decision policy is to find the optimal transition time that maximizes expected reward. The reward on a particular trial for wins ($R_{win}$), indecisions ($R_{indecision}$), and incorrects ($R_{incorrect}$) is,
% Expected Reward
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0.
\end{equation}

The expected reward is defined as the reward of a trial outcome multiplied by the probability of that outcome, which is
%
\begin{align}
    \mathbb{E}[R|\tau] = & P(Win|\tau) \cdot R_{Win} \nonumber \\ &+ P(Incorrect|\tau) \cdot R_{Incorrect} \nonumber \\ &+ P(Indecision|\tau) \cdot R_{Indecision}.
\end{align}

The decision policy uses known parameters to select an optimal transition time $\tau^*$ that maximizes expected reward:
% Maximize expected reward with tau
\begin{equation}
    \tau^* = \underset{\tau}{argmax}[\mathbb{E}(R|\tau)].
\end{equation}

@@

We used both a warm-start initialization and bootstrap procedure (see below) to determine the switch time mean ($\mu_{switch}$) and uncertainty ($\sigma_{switch}$), as well as the decision policy’s knowledge of the switch time mean ($\hat{\mu}_{switch}$), switch time uncertainty ($\hat{\sigma}_{switch}$), and timing uncertainty ($\hat{\sigma}_{\tau}$).

@@

\noindent The fitting procedure for the Full Switch Time Model and Partial Switch Time Model began with a “warm-start” to find an initial set of $\mu_{switch}$, $\sigma_{switch}$, $\hat{\mu}_{switch}$, $\hat{\sigma}_{switch}$, and $\hat{\sigma}_{\tau}$ \autocite*{rothReinforcementbasedProcessesActively2023,rothPunishmentLeadsGreater2024}.  Here the remaining parameters estimated from experimental data were set as the group level means. We found the best-fit parameters that led to the lowest loss between model outputs ($Model_{i,j}$) and group data means ($Data_{i,j}$) according to
% Loss Equation 
\begin{equation}
    \mathcal{L} = \sum_{i = 1}^{6} \sum_{j = 1}^{5} \frac{|Data_{i,j} - Model_{i,j}|}{Data_{i,j}},
\end{equation}
where $i$ corresponds to experimental condition and $j$ corresponds to each dependent measure (i.e., movement onset, standard deviation of participant movement onset, wins, indecisions, and incorrects). The fitting procedure was repeated 1,000 times to avoid local minimums. From these 1,000 optimizations, we used the set of parameters that resulted in the lowest loss as the initial guess for our bootstrap procedure. Model fitting was performed using the Powell algorithm in the Minimize function from the Scipy Python library.

@@

The Partial Switch Time Model fit the timing uncertainty, switch time mean, switch time uncertainty. Critically, this model did not have full knowledge of these parameters, so the value that the decision policy used to select the optimal time was fit separately from the value that was used to determine the model outputs. Note that the timing uncertainty value used for model outputs is from experimental data, but this model allowed the knowledge of the timing uncertainty to be a fit parameter. The values that were used for model outputs were: timing uncertainty (77.83 ms; [69.4, 86.8]), switch time mean (21.10 ms; [1.46, 63.71]), switch time uncertainty (134.73 ms; [111.22, 155.06]. The values that were used by the decision policy were: timing uncertainty (1.65 ms;  [0.08, 4.63]), switch time mean (9.0 ms; [0.00, 16.65]), switch time uncertainty (40.4 ms; [34.54, 48.02]). Critically, the fitting procedure for the Partial Switch Time Model selected the decision policy’s values for the switch time mean, switch time uncertainty, and timing certainty to be less than the values that impact the model outputs, indicating that  humans have imperfect knowledge of these parameters.
